On Secure Delegation of SampBQP with a Classical Client

### 2020-01-23 preliminaries.tex
Updates from Overleaf

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms \hannote{ protocols?} $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is run by the prover, a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
		\item $\bbV$ is run by the verifier, which is a hybrid machine of a classical part and a limited quantum part. The classical part is a $\BPP$ machine. The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel which can transmit $\tau$ qubits. At any given time, the verifier is not allowed to possess more than $\tau$ qubits. The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
		 \item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially\hannote{poly in what} many bits to either direction. 
		 \item The protocol\hannote{?} is run by steps. At any given step, either the verifier or the prover performs computations on their registers and send bits and qubits through the relevant channels to the other party.	\hannote{redundant?} 
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$ outputs a distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

@@

\begin{dfn}
	A quantum homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

@@

\begin{dfn}
	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$. Then it is IND-CPA secure if any polynomial time adversary $\cA$ can't win \protoref{protoIndCPA} with probability better than $\frac{1}{2}+\negl(\lambda)$ \Ethan{Check if it's actually lambda}
\end{dfn}

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	\begin{algorithmic}[1]
		\State \Ethan{Do we need some kinda generalization of Keygen here...?}
		\State $\cA$ picks strings $c_1$ and $c_2$ and sends them to the challenger
		\State The challenger picks $c_b$ at random where $b\in\set{0,1}$
		\State The challenger runs the protocol with the adversary, acting as the verifier with input $c_b$
		\State $\cA$ attempts to guess $b$
	\end{algorithmic}
\end{algorithm}
\floatname{algorithm}{Algorithm}

>>>>

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_\tau$ with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms \hannote{ protocols?} $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is run by the prover, a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
		\item $\bbV$ is run by the verifier, which is a hybrid machine of a classical part and a limited quantum part. The classical part is a $\BPP$ machine. The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel which can transmit $\tau$ qubits. At any given time, the verifier is not allowed to possess more than $\tau$ qubits. The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
		 \item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially\hannote{poly in what} many bits to either direction. 
		 \item The protocol\hannote{?} is run by steps. At any given step, either the verifier or the prover performs computations on their registers and send bits and qubits through the relevant channels to the other party.	\hannote{redundant?} 
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) For all $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$ outputs a distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

@@

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

@@

\begin{dfn}
	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$. Then it is IND-CPA secure if, for any $x_1, x_2$, any polynomial time adversary $\cA$,
	$$\abs{\Pr\left[TODO\right]}-TODO$$

\end{dfn}

### 2020-01-23 qpip0.tex
Updates from Overleaf

\subsection{Subprotocol for Quantum Measurements}
%\hannote{what is this for?}
As a warm-up, we  restate the construction in \cite{mahadev_delegation}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.

@@

\begin{theorem}
    \label{Mahadev_QPIP0_Protocol_Interface}
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
	\begin{itemize}
	    \item The protocol runs either a ``Hadamard round" or a ``test round".
	    \item With a test round, the verifier outputs nothing other than accept/reject
	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
	    \item (completeness) $\forall n\in\mathcal{B}^{\otimes n}, h\in\bbN$ and $h$, there is a prover with negligible reject probability. Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_\rho, h$
	    \item (soundness) Fix $\bbP'$ and $h$. Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round. Then $\exists\tilde\bbP$ s.t. $\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t. $D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
		\item This is a 4-round protocol. The prover does not know whether it is a test or Hadamard round until the end of 3rd round.
		\begin{enumerate}
			\item The verifier generates $(k, td)$, ``key" and ``trapdoor". It sends the key to the prover.
			\item The prover computes a classical ``commitment" $y$ and sends it to the verifier.
			\item The verifier sends $c\in\set{0, 1}$, where $c=0$ corresponds to test round and $c=1$ corresponds to Hadamard round.
			\item The prover computes and sends a classical string $a$
		\end{enumerate}
	\end{itemize}
\end{theorem}

@@

\hannote{duplicate version by ethan..}
\begin{lem}
	Let $(U_0, U)$ be some prover's strategy.
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $i\in[m]$, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma$ be sampled uniformly from $\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document}.
	Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{X, Z}$,

@@

	where $t$ is the number of qubits in the register $ph$ \Ethan{Where is this register defined?},
	$z_0, z_1\in\bbC$ such that $\abs{z_0}=\abs{z_1}=1$, and $z_0$, $z_1$, $\ket{\psi_0}_{X, Z}$, $\ket{\psi_1}_{X, Z}$, $\ket{\psi_{err}}_{X, Z}$ may depend on $\gamma$.
	Furthermore, the following properties are satisfied.
	\begin{enumerate}
		\item Let $\ket{\psi_{err}}=\ket{\psi}-\ket{\psi_0}-\ket{\psi_1}$, then
			$$\E_\gamma[\norm{\ket{\psi_{err}}}^2]\leq\frac{1}{T}+\negl(n)$$
		\item TODO Some long property
		\item For any fixed $\gamma$,
			$$\E_{b\in\set{0, 1}}\left[\norm{\ket{\psi_{b}}_{X, Z}}^2\right]\leq\frac{1}{2}\norm{\ket{\psi}_{X, Z}}^2$$
		\item For any fixed $\gamma$ and $c\in\set{0, 1}^m$ such that $c_i=0$, \Ethan{Where's this $M_{X_i}$ defined?}
			$$\Pr\left[M_{X_i}\circ U\frac{\ket{c}_C\ket{\psi_0}_{X,Z}}{\norm{\psi_0}_{X,Z}}\in A_{k_i, y_i}\right]\leq2^{m-1}\gamma+\negl(n)$$
		\item For any fixed $\gamma$, there exists an efficient quantum algorithm $\cE_i$ such that
			$$\Pr\left[\cE_i\left(\frac{\ket{0^m}_C\ket{\psi_1}_{X,Z}}{\norm{\psi_1}_{X,Z}}\in A_{k_i, y_i}\right)\right]\leq1-\negl(n)$$
	\end{enumerate}
\end{lem}

@@

\end{theorem}
\begin{proof}
We run Mahadev's 4-round protocol \ref{} and use parallel repetition to reduce the soundness error.
\end{proof}

\begin{lem}
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma_i\xleftarrow{\$}\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document} for each $i\in[m]$.
	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
	$$\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ket{\psi_{110}}+\ldots+\ket{\psi_{11\ldots10}}+\ket{\psi_{11\ldots11}}+\ket{\psi_{err}}$$
	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
	Furthermore, the following properties are satisfied. \Ethan{Takes a bit of parsing to see how is our case different here since $c$ might be defined differently for us}
	\begin{enumerate}
		\item stuff
		\item For any fixed $\hat\gamma$... 
		\item For any fixed $\hat\gamma$...
		\item For any fixed $c$,
			$$\E_{\hat\gamma}\left[\norm{\ket{\psi_{err}}_{X,Z}}^2\right]\leq\frac{6m^2}{T}+\negl(n)$$
		\item stuff
	\end{enumerate}
\end{lem}
    asdf
\begin{theorem}

@@

\end{theorem}

>>>>

\subsection{Subprotocol for Quantum Measurements}
\hannote{Ethan old description before parallel rep.}
As a warm-up, we  restate the construction in \cite{mahadev_delegation}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.

@@

\begin{theorem}
    \label{Mahadev_QPIP0_Protocol_Interface}
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
	\begin{itemize}
	    \item The protocol runs either a ``Hadamard round" or a ``test round".
	    \item With a test round, the verifier outputs nothing other than accept/reject
	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
	    \item (completeness) $\forall\rho\in\mathcal{B}^{\otimes n}$ and $h\in\set{0,1}^n$, there is a prover with negligible reject probability. Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_{\rho, h}$
	    \item (soundness) Fix $\bbP'$ and $h$. Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round. Then $\exists\tilde\bbP$ s.t. $\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t. $D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
		\item This is a 4-round protocol. The prover does not know whether it is a test or Hadamard round until the end of 3rd round.
		\begin{enumerate}
			\item The verifier generates $(k, td)$, ``key" and ``trapdoor". It sends the key to the prover.
			\item The prover computes a classical ``commitment" $y$ and sends it to the verifier.
			\item The verifier sends $c\in\set{0, 1}$, where $c=0$ corresponds to test round and $c=1$ corresponds to Hadamard round.
			\item The prover computes and sends a classical string $a$
		\end{enumerate}
	\end{itemize}
\end{theorem}

\hannote{import urmila protocol description.. up}
Here, we recall the Mahadev's protocol \cite{FOCS:Mahadev18a}. We only give a high-level description of the protocol and properties of it and omit the details since they are not needed to show our result.

The protocol is run between a quantum prover $\pro$ and a classical verifier $\ver$ on a common input $x$. The aim of the protocol is to enable a verifier to classically verify $x\in \lang$ for a BQP language $\lang$ with the help of interactions with a quantum prover.
The protocol is a 4-round protocol where the first message is sent from $\ver$ to $\pro$. 
We denote the $i$-th message generation algorithm by $\ver_i$ for $i\in\{1,3\}$ or $\pro_i$ for $i\in \{2,4\}$ and denote the verifier's final decision algorithm by $\ver_\out$.
Then a high-level description of the protocol is given below.
\begin{description}
\item[$\ver_1$:] On input the security parameter $1^\secpar$ and $x$, it generates a pair $(\key,\td)$ of a``key" and ``trapdoor", sends $\key$ to $\pro$, and keeps $\td$ as its internal state.
\item[$\pro_2$:] On input $x$ and $\key$, it generates a classical ``commitment" $\comy$ along with a quantum state $\ket{\st_\pro}$, sends $\comy$ to $\pro$, and keeps $\ket{\st_\pro}$ as its internal state.
\item[$\ver_3$:] It randomly picks $c\sample \bit$ and sends $c$ to $\pro$.\footnote{The third message is just a public-coin, and does not depend on the transcript so far or $x$.}
Following the terminology in \cite{FOCS:Mahadev18a}, we call the case of $c=0$ the ``test round" and the case of $c=1$ the ``Hadamard round".
\item[$\pro_4$:] On input $\ket{\st_\pro}$ and $c$, it generates a classical string $\ans$ and sends $\ans$ to $\pro$.
\item[$\ver_\out$:] On input $\key$, $\td$, $y$, $c$, and $\ans$, it returns $\top$ indicating acceptance or $\bot$ indicating rejection.
In case $c=0$, the verification can be done publicly, that is, $\ver_\out$ need not take $\td$ as input.
\end{description}

For the protocol, we have the following properties:\\
\noindent\textbf{Completeness:}
For all $x\in \lang$, we have $\Pr[\langle \pro,\ver \rangle(x)]=\bot]= \negl(\secpar)$.\\
\noindent\textbf{Soundness:}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$, we have  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot]\leq 3/4$.

We need a slightly different form of soundness implicitly shown in \cite{FOCS:Mahadev18a}, which roughly says that if a cheating prover can pass the ``test round" (i.e., the case of $c=0$) with overwhelming probability, then it can pass the ``Hadamard round" (i.e., the case of $c=1$) only with a negligible probability. 
\begin{lemma}[implicit in \cite{FOCS:Mahadev18a}]\label{lem:Mah_soundness}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$ such that  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot\mid c=0]=\negl(\secpar)$, we have $\Pr[\langle \pro^*,\ver \rangle(x)]=\top\mid c=1]=\negl(\secpar)$.
\end{lemma}

We will also use the following simple lemma:
\begin{lemma}\label{fact:perfectly_pass_test}
There exists an efficient prover that passes the test round with probability $1$ (but passes the Hadamard round with probability $0$) even if $x\notin \lang$. 
\end{lemma}

@@

\iffalse
\hannote{duplicate version by ethan..}
\begin{lem}
	Let $(U_0, U)$ be some prover's strategy.
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $i\in[m]$, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma$ be sampled uniformly from $\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document}.
	Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{X, Z}$,

@@

	where $t$ is the number of qubits in the register $ph$ \Ethan{Where is this register defined?},
	$z_0, z_1\in\bbC$ such that $\abs{z_0}=\abs{z_1}=1$, and $z_0$, $z_1$, $\ket{\psi_0}_{X, Z}$, $\ket{\psi_1}_{X, Z}$, $\ket{\psi_{err}}_{X, Z}$ may depend on $\gamma$.
	Furthermore, the following properties are satisfied.
	\begin{enumerate}
		\item Let $\ket{\psi_{err}}=\ket{\psi}-\ket{\psi_0}-\ket{\psi_1}$, then
			$$\E_\gamma[\norm{\ket{\psi_{err}}}^2]\leq\frac{1}{T}+\negl(n)$$
		\item TODO Some long property
		\item For any fixed $\gamma$,
			$$\E_{b\in\set{0, 1}}\left[\norm{\ket{\psi_{b}}_{X, Z}}^2\right]\leq\frac{1}{2}\norm{\ket{\psi}_{X, Z}}^2$$
		\item For any fixed $\gamma$ and $c\in\set{0, 1}^m$ such that $c_i=0$, \Ethan{Where's this $M_{X_i}$ defined?}
			$$\Pr\left[M_{X_i}\circ U\frac{\ket{c}_C\ket{\psi_0}_{X,Z}}{\norm{\psi_0}_{X,Z}}\in A_{k_i, y_i}\right]\leq2^{m-1}\gamma+\negl(n)$$
		\item For any fixed $\gamma$, there exists an efficient quantum algorithm $\cE_i$ such that
			$$\Pr\left[\cE_i\left(\frac{\ket{0^m}_C\ket{\psi_1}_{X,Z}}{\norm{\psi_1}_{X,Z}}\in A_{k_i, y_i}\right)\right]\leq1-\negl(n)$$
	\end{enumerate}
\end{lem}
\fi

@@

\end{theorem}
\begin{proof}
We run Mahadev's 4-round protocol \ref{} and use parallel repetition to reduce the soundness error. \hannote{describe $N$ time para rep}. 
\end{proof}

\begin{lem}
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma_i\xleftarrow{\$}\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document} for each $i\in[m]$.
	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
	$$\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ket{\psi_{110}}+\ldots+\ket{\psi_{11\ldots10}}+\ket{\psi_{11\ldots11}}+\ket{\psi_{err}}$$
	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
	Furthermore, the following properties are satisfied. \Ethan{Takes a bit of parsing to see how is our case different here since $c$ might be defined differently for us}
	\begin{enumerate}
		\item stuff
		\item For any fixed $\hat\gamma$... 
		\item For any fixed $\hat\gamma$...
		\item For any fixed $c$,
			$$\E_{\hat\gamma}\left[\norm{\ket{\psi_{err}}_{X,Z}}^2\right]\leq\frac{6m^2}{T}+\negl(n)$$
		\item stuff
	\end{enumerate}
\end{lem}
    asdf
\begin{cor}

@@

\end{cor}
